Reanalysis Step 2: Multiple Imputation

### 2025-08-19 reanalysis-2-multiple_imputation.qmd
Deal with MI merge warnings

df_mice <- df_for_imputation |>
  dplyr::select(dplyr::all_of(imputation_vars)) |>
  mutate(
    # Convert person_dr to ordered factor for polr imputation method
    person_dr = factor(person_dr, levels = c(0, 1, 2), 
                      labels = c("No_DR", "NPDR", "PDR"),
                      ordered = TRUE)
  )
```

@@

  # Add these variables back to each imputed dataset
  imputed_datasets <- lapply(imputed_datasets, function(imp_data) {
    imp_data <- imp_data |>
      left_join(
        df_original_full |> 
          dplyr::select(e_mrn_deidentified, dplyr::all_of(vars_to_add)),
        by = "e_mrn_deidentified"
      )

>>>>

df_mice <- df_for_imputation |>
  dplyr::select(dplyr::all_of(imputation_vars)) |>
  mutate(
    # Convert person_dr to ordered factor for polr imputation method
    person_dr = factor(person_dr, levels = c(0, 1, 2), 
                      labels = c("No_DR", "NPDR", "PDR"),
                      ordered = TRUE),
    # Lock factor levels for categorical variables to ensure consistency
    gender_cat = factor(gender_cat),
    race_ethnic_cat = factor(race_ethnic_cat),
    insurance_cat = factor(insurance_cat)
  )
```

@@

  # Add these variables back to each imputed dataset
  imputed_datasets <- lapply(imputed_datasets, function(imp_data) {
    imp_data <- imp_data |>
      left_join(
        df_original_full |> 
          dplyr::select(e_mrn_deidentified, dplyr::all_of(vars_to_add)),
        by = "e_mrn_deidentified",
        relationship = "many-to-many"  # Expected: multiple eyes per patient
      )
